Replication Survey

### 2024-01-19 docs/manuscript/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Attempting to replicate a study is a means of critically assessing whether the evidence provided by the researchers that conducted the study support the claims they make and their explanation of a phenomenon. 
Replications confront existing explanations with new evidence by retesting prior claims using new data, while typically controlling for procedural differences by conducting similar analyses.
Replications can be designed to serve epistemic functions and to test several forms of validity.
Attempts to reproduce prior research also retest claims, but do so using the same data and the same, or very similar, analyses. 
The central focus a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories underlying it \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, the claims of the prior study, the data and methods used, and the current understanding of the phenomena may be brought into question \citep{christensen2019, NASEM2019}.

While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography.
The majority of recent research in the geographic literature on the subject has focused on reproduction over replication, and has emphasized the computational reproducibility of geographic research ahead of other dimensions.
For example, an ongoing reproducibility initiative supported by the Association of Geographic Information Laboratories in Europe annually attempts to reproduce the computational results of submissions to their annual meeting and reports on the accessibility of related data, code, and computational environment \citep{nust2018, ostermann2021}.
A series of reproduction studies led by Kedron and Holler \citep{Kedron2023Beyond, Kedron_Holler_Bardin_Hilgendorf_2022} advance this stream of work by introducing selected variations into the reproduction process to test the sensitivity of results to conceptual and methodological perturbations. 
However, those studies also largely focus on testing the conclusion and internal validity of past studies through computational reproduction.

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
With those intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility, whether the same results can be created using the same data and methods, rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
In the remainder of this paper, we detail the design of our survey, sampling strategy, and analytical approach before presenting the results of our survey. 
We then discuss the implications and limitations of our work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Broadly defined, a replication study is any study that has at least one outcome that would be considered diagnostic evidence of a claim from prior research, and can be used to assess the validity of prior claims \citep{nosek2020}.
More narrowly, replication studies are differentiated by the alterations they make to a study, which is linked to the epistemological function they are intended to serve.
By altering different aspects of a study a researcher attempting a replication can use their finding to potentially assess (1) conclusion, (2) internal, (3) construct, and (4) external validity \citep[see][]{schmidt2009, gomez2010replications, radder2003, radder2012}.

OLD: Replications provide evidence of the credibility of claims across conditions that either naturally or are purposefully manipulated to differ from the original study.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion and Conclusion}
The results of our survey suggest geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
However, we also found that researcher provided definitions often did not clearly articulate the epistemological role, or roles, that could be played by a replication study. 
Researcher definitions instead focused on criteria used to identify a study as a replication. 
This same focus on criteria can be observed in the wider R\&R literature, where authors typically gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices. 
This tendency toward criteria may suggest that replication as an epistemological tool is not be at the forefront of geographic researchers' thinking about replication.
While this finding aligns with the observable focus on computational forms of reproducibility in the geographic literature, further data is needed to support this conclusion because it may simply be the case that respondents could not provide sufficient definitional nuance in a survey text response.

It also remains unclear if or how geographic researchers map variations between an original study and its replication to the epistemological functions that replication study is intended to serve.
A clear understanding of this connection between variations and functions is essential because which aspects of a study are changed controls the form of validity being assessed \citep{gomez2010replications, radder2003, schmidt2009}.
Poor documentation and articulation of these connections in replication studies of geographic research could lead to the misinterpretation of the results of an individual replication, and could misdirect the collective assessment of a claim across a set of replication studies.
Developing a schema to map replication study variations to functions may be particularly challenging in geography due to the complexity of geographic systems and the limited control researchers have over those systems. 
Moreover, it is often unclear which aspect of a study are changing when a replication study is conducted in a new location. 
For example, when a researcher conducting a replication collects new data from a new location it may be difficult to determine whether the study is testing the external validity of a claim in a new population, or in the same population that is subjected to different place-based processes.
Our results suggest that a conceptual treatment of these connections attuned to the peculiarities of spatial data analysis would be an important first step toward conducting and systematically assessing interpretable replication studies of geographic research.

@@

Building on the differences that exist between research traditions in geography, it may be fruitful to further examine how researcher working in different subfield precieve and use replication in the work. 
Overall, the differences in responses we observed across subfields and methodological approaches was small, but this finding should be interpreted with caution given sizes of our subfield samples.
However, it is sensible that responses to questions about barriers to replicability and motivations to attempt replications would be similar between groups because researchers across the discipline work in similar academic incentive systems. 
One notable exception to this consistency was our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Limitations and Future Research} 
Survey research has several common limitations which we attempted to mitigate through the design of our study. 
Unlike prior surveys of reproducibility and replicability, our study uses a sampling frame designed to be representative of our target population of active geographic researchers. 
However, use of a well-constructed sampling frame and probability sampling do not ensure that a balanced and representative sample will be drawn from the target population. 
Ideally, we would stratify our potential respondents into meaningful subgroups, randomly draw participants from these subgroups, and use a post-stratification procedure to address any imbalance in our response. 
However, we could not follow this approach because stratification require knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
We did not have access to this information because we presently lack a comprehensive understanding of replicability in geography and no list of geographic researchers complete with relevant predictor information exists.
Given these limitations, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.

We have similarly worked to reduce the effects of several other common forms of bias from our survey.
We have worked to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five year period.
However, geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
Geographic researchers that have only published outside geographically indexed journals would not be captured in our sampling frame which would create exclusion errors. 
However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to have published at least one study in the journals meeting our inclusion criteria.

@@

Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
Our work provides an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications. 
However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changes in a replication study.
Future research using in-depth interviews or multi-analyst study designs could probe these question more deeply. 
It would also be useful to track the information collected in this survey over time and to link that tracking to specific topics. 
For example, understanding how researcher perspectives on the epistemological function of replication shift in climate change impacts research may be a useful indicator of how well researchers in that field are developing theories and methodologies capable of dealing with increasing variation and shifting baselines induced by climate change.
More broadly, regular monitoring of perceptions of replication would help identify areas in need of engagement, as well as the success or failure of past investments designed to enhance R\&R.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Replications confront existing explanations with new evidence by retesting prior claims using new data, while controlling for procedural differences by conducting similar analyses.
Replications can be designed to serve different epistemic functions and to test several forms of validity.
Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.

While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography.
The majority of recent research in the geographic literature on the subject has focused on reproduction over replication, and has emphasized the computational reproducibility of geographic research ahead of other dimensions.
For example, an ongoing reproducibility initiative supported by the Association of Geographic Information Laboratories in Europe attempts to reproduce the computational results of submissions to their annual meeting and reports on the accessibility of related data, code, and computational environment \citep{nust2018, ostermann2021}.
A series of reproduction studies led by Kedron and Holler \citep{Kedron2023Beyond, Kedron_Holler_Bardin_Hilgendorf_2022} advance this stream of work by introducing selected variations into the reproduction process to test the sensitivity of results to conceptual and methodological perturbations. 
However, those studies also largely focus on testing the conclusion validity of past studies through computational reproduction.

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
With these intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.

In the remainder of this paper, we first briefly present the epistemic roles of replication in the context of geographic research.
We then detail the design of our survey, sampling strategy, and analytical approach before presenting our results. 
We conclude with a discussion of the implications and limitations of our work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Replications structure the iterative development of theory by confronting claims with new evidence.
Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings. 
Until tested, whether a claim is expected to hold under new conditions is either a product of the theory used to structure the original investigation, or a speculative assumption of generalizability.
Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.  
By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.

The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}. 
Replication studies are often classified either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.

Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, the replication is designed to assess conclusion validity.
As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation. 
Alternatively, a researcher can use a replication to test construct validity, if they change how a key construct is measured and also hold all other aspects of a study constant. 
Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made. 
Finally, when the materials and procedures (e.g., data collection device, analyses) used in a replication differ from an initial study, the replication assesses the whether these factors affected the original results testing the internal validity of the prior work.

In conceptual replications changes are made to the population or location being studied to test external validity and whether the claims made in a study generalize to new populations and contexts. 
In geographic research, a conceptual replication could for example involve changing the location of a study from one city to another, or one ecosystem to another. 
Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after a migration event is through to have changed the population of that area. 
Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
For example, it is not necessarily the case that observing evidence in a one location that contradicts a claim made in study of another location would cause a researcher to reduce their confidence in that initial claim.

As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015}.
When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Replicability of Geographic Research}
Geographers have arguably never formally and explicitly held an extended discussion of the role of replication in the discipline.
However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{inkpen2013science, harvey1969, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}. 
Within this literature, discussions of replication typically pivot on the expected variability of processes across locations, whether replications can inform theory development and, as a practical matter, the ability to control factors that may affect the outcome of a study.

The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space implying that observable differences between places, and perhaps an inability to replicate prior findings, should be expected across locations. 
Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different location is or is not determined by the same processes.  
In some instances, commentary about differences between locations are extended to point out the uniqueness of places and mixed with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}. 
Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.

Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967} which, applied to locations, alternatively argues that phenomena studied in space cannot be encountered twice, or that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features. 
The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features in different locations, or even to encounter the same arrangement of features at different times in the same location.
In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
In this situation, findings may be expected to replicate and attempting replications can give insight into the stability of processes across locations.

Understanding places as defined by process that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations. 
In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds. 
In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.

Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations, but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}. 
In practice, geographers often lack the ability to control where data is collected, which populations are included or excluded in a study, how variables are measured, and the materials and procedures used when attempting a replication.
This lack of control makes it difficult to execute replications that isolate the influence of any particular factor, which makes it unclear what lessons should be learned from a replication attempt and what epistemological function that attempt may be serving. 
Moreover, it is also often unclear which factors should be accounted for when studying a particular location.
As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatially heterogeneity.
While these factors make replication practically challenging in some forms of geographic research, they do not themselves eliminate the potential usefulness of the practice in selected cases.

Geography as a discipline is presently defined by its topical, epistemological, and methodological diversity. 
While replication has been an implicit part of many discussions of the development of knowledge in the discipline, how exactly the practice is understood and applied by researchers within those different traditions remains unclear.
Moreover, to date there has been no empirical measure of how often researchers across the discipline attempt to replicate research, what motivates them to pursue or not pursue replications, and how they would interpret the findings of such studies. 
In fact, we expect that many geographic researcher would disagree with the conception and presentation of replication presented above. 
However, until researcher conceptions and practices of replication are measured conversations about the role of replication in the discipline can only progress so far.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion and Conclusion}
The results of our survey suggest geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
However, we also found that researcher provided definitions often did not clearly articulate the epistemological role, or roles, that could be played by a replication study. 
Researcher definitions instead focused on criteria used to identify a study as a replication. 
Indeed, many of these definitions closely aligned with the definition of reproducibility, which mirrors  \cite{kedron2023survey} findings that researchers appear to often conflate these two terms. 
This same focus on criteria can be observed in the wider R\&R literature, where authors typically gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices. 
This tendency toward criteria may suggest that replication as an epistemological tool is not at the forefront of geographic researchers' thinking about replication.
While this finding aligns with the observable focus on computational forms of reproducibility in the geographic literature, further data is needed to support this conclusion because it may simply be the case that respondents could not provide sufficient definitional nuance in a survey text response.

It also remains unclear if or how geographic researchers map variations between an original study and its replication to the epistemological functions that replication study is intended to serve.
A clear understanding of the connection between variations and functions is essential because which aspects of a study are changed controls the form of validity being assessed \citep{gomez2010replications, radder2003, schmidt2009}.
Poor documentation and articulation of these connections in replication studies of geographic research could lead to the misinterpretation of the results of an individual replication, and could misdirect the collective assessment of a claim across a set of replication studies.
Developing a schema to map replication study variations to functions may be particularly challenging in geography due to the complexity of geographic systems and the limited control researchers have over those systems. 
Moreover, it is often unclear which aspect of a study are changing when a replication study is conducted in a new location. 
For example, when a researcher conducting a replication collects new data from a new location it may be difficult to determine whether the study is testing the external validity of a claim in a new population, or in the same population that is subjected to different place-based processes.
Our results suggest that a conceptual treatment of these connections attuned to the peculiarities of spatial data analysis would be an important first step toward conducting and systematically assessing interpretable replication studies of geographic research.

@@

Finally, building on the differences that exist between research traditions in geography, it may be fruitful to further examine how researchers working in different subfields perceive and use replication in their work. 
Overall, the differences in responses we observed across subfields and methodological approaches was small, but this finding should be interpreted with caution given the sizes of our subfield samples.
It is sensible that responses to questions about barriers to replicability and motivations to attempt replications would be similar across subfields because researchers across the discipline work in similar academic incentive systems.
Alternatively, there are substantial differences in the concepts and methods used in different subfields, in the types of questions researchers ask, and the phenomena and systems they study. 
It seems natural that this variation in practice would translate into the use and implementation of replications. 
However, the limited size of the sample of researchers that reported actually attempting replications did not allow for an extensive analysis of this questions by subfield. 
Perhaps an initial indicator of these differences is our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Limitations and Future Research} 
Survey research has several common limitations which we attempted to mitigate through the design of our study. 
Unlike prior surveys of reproducibility and replicability, our study uses a sampling frame designed to be representative of our target population of active geographic researchers. 
However, use of a well-constructed sampling frame and probability sampling do not ensure that a balanced and representative sample will be drawn from the target population. 
Ideally, we would stratify our potential respondents into meaningful subgroups, randomly draw participants from these subgroups, and use a post-stratification procedure to address any imbalance in our response. 
However, we could not follow this approach because stratification requires knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
We did not have access to this information because we presently lack a comprehensive understanding of replicability in geography and no list of geographic researchers complete with relevant predictor information exists.
Given these limitations, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.

We have similarly worked to reduce the effects of several other common forms of bias from our survey.
We have worked to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five year period.
However, geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
Geographic researchers that have only published outside geographically indexed journals would not be captured in our sampling frame which would create exclusion errors. 
We believe the number of individuals falling into this category will be small as most active geographic researchers are likely to have published at least one study in the journals meeting our inclusion criteria.

@@

Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
This work offers an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications. 
However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changes in a replication study.
Future research using in-depth interviews or multi-analyst study designs could probe these question more deeply. 
It would also be useful to track the information collected in this survey over time and to link that tracking to specific research topics. 
For example, understanding how researcher perspectives on the epistemological function of replication shift in climate change impacts research may be a useful indicator of how well researchers in that field are developing theories and methodologies capable of dealing with increasing variation and shifting baselines induced by climate change.
More broadly, regular monitoring of perceptions of replication would help identify areas in need of engagement, as well as the success or failure of past investments designed to enhance R\&R.
